Penalized regression for left-truncated and right-censored survival data

### 2021-04-30 manuscript.tex
minor edit

The extension of penalized regression methods to survival data have been extensively described and applied, for example in microarray gene expression data \cite{gui2005penalized}, transcriptomes \cite{wu2011penalized}, and injury scale codes \cite{mittal2013penalized}. Like linear regression, the performance and fit of a Cox proportional hazards model is known to deteriorate with large $p$, providing an advantage to penalized approaches in high-dimensional, time-to-event feature sets.

>>>>

The extensions of penalized regression methods to survival data have been extensively described and applied, for example in microarray gene expression data \cite{gui2005penalized}, transcriptomes \cite{wu2011penalized}, and injury scale codes \cite{mittal2013penalized}. Like linear regression, the performance and fit of a Cox proportional hazards model is known to deteriorate with large $p$, providing an advantage to penalized approaches in high-dimensional, time-to-event feature sets.
